Cell-DNA Standard Curves

### 2021-03-20 inst/analysis/dna-per-cell.Rmd
complete extracellular fluxes analysis

cells_per_dna  %>% 
  knitr::kable(
    digits = 4, 
    col.names = c("Cell Type", "Volume", "Cell / DNA"), 
    align = "c", 
    booktabs = TRUE
  ) %>% 
  kableExtra::kable_styling(position = "center") 
```

>>>>

cells_per_dna  %>% 
  my_kable(
    digits = 0, 
    col.names = c("Cell Type", "Volume", "Cell / DNA"), 
    align = "c", 
    caption = "Cells per DNA (ng)"
  ) %>% 
  kableExtra::kable_styling(position = "center") 
```
